Data Management for LSST Special Programs

### 2024-03-27 sec_proc.tex
fix typo

\textbf{Alert production is restricted -- }
As processed visit images will embargoed for 80 hours,
only official Rubin Prompt processing may produce alerts.
No User-Generated Processing may contribute alerts to the LSST alert stream.

>>>>

\textbf{Alert production is restricted -- }
As processed visit images will be embargoed for 80 hours,
only official Rubin Prompt processing may produce alerts.
No User-Generated Processing may contribute alerts to the LSST alert stream.
